---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-26"
output: html_document
---

## Dataset: Invasive Neophyten

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100043)

Auto generated R starter code for data set 100043.

## Metadata

- **Dataset_identifier** `100043`
- **Title** `Invasive Neophyten`
- **Description** `Die im Kanton Basel-Stadt am häufigsten vorkommenden invasiven Neophyten (nicht heimische, problematische Pflanzenarten) wurden kartiert und die Fundorte je nach Pflanzenart als Flächen oder Punkte aufgenommen. Die Kartierung wurde bisher in den Jahren 2006, 2009 und 2013 durchgeführt.`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2019-11-06`
- **Modified** `2024-06-26T05:03:53+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `2005-12-31T23:00:00+00:00`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Raum und Umwelt', 'Geographie']`
- **Keywords** `['Pflanzen', 'Einheimisch', 'Auswärtig', 'Einwanderung', 'Verdrängen', 'Invasion', 'Naturschutz']`
- **Publisher** `Stadtgärtnerei`
- **Reference** `www.geo.bs.ch/invasive_neophyten; https://www.geocat.ch/geonetwork/srv/ger/catalog.search#/metadata/8ac0414e-a6ff-4d4f-ad45-0af150f94a85`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Create directory if it does not exist
  data_path <- file.path(getwd(), '..', 'data')
  if (!dir.exists(data_path)) {
    dir.create(data_path, recursive = TRUE)
  }
  # Download the CSV file
  csv_path <- file.path(data_path , '100043.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
  )
  # if dataframe only has one column or less the data is not ";" separated
  if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
  }
  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100043/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
