---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-25"
output: html_document
---

## Dataset: Defibrillatoren

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100019)

Auto generated R starter code for data set 100019.

## Metadata

- **Dataset_identifier** `100019`
- **Title** `Defibrillatoren`
- **Description** `Sämtliche Standorte öffentlich zugänglicher Defibrillatoren in Basel-Stadt sind im Geoportal und in der First Responder App einsehbar. Die entsprechenden Standorte sind mit einem grünen Herz-Symbol signalisiert. Finden Sie den nächsten Defibrillator in Ihrer Nähe.`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2019-11-06`
- **Modified** `2024-06-25T05:02:59+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `None`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Gesundheit', 'Geographie']`
- **Keywords** `['Notfall', 'Reanimation', 'CPR', 'Herz', 'Lunge', 'Wiederbelebung', 'Standort']`
- **Publisher** `Rettung`
- **Reference** `www.geo.bs.ch/defibrillatoren; https://www.geocat.ch/geonetwork/srv/ger/catalog.search#/metadata/31d03929-dd6d-4267-872e-a423d27fc6a4`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Download the CSV file
  csv_path <- file.path(getwd(), '..', 'data', '100019.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
    read.csv(csv_path, sep = ",", stringsAsFactors = FALSE, encoding = "UTF-8"),
    warning = function(w) NULL,
    error = function(e) NULL
  )

  # If the dataframe has one column or less, try with semicolon as separator
  if (is.null(data) || ncol(data) <= 1) {
    data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
    )

    if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
    }
  }

  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100019/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
