---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - DCC Data Competence Center"
date: "2026-02-01"
output: html_document
---

## Dataset: Umweltanalyse Oberflächengewässer

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100066)

Auto generated R starter code for data set 100066.

## Metadata

- **Dataset_identifier** `100066`
- **Title** `Umweltanalyse Oberflächengewässer`
- **Description** `<p>Der Datensatz enthält die Analysedaten der Beprobungen der Oberflächengewässer des Kantons Basel-Stadt seit dem Jahr 1993. Die Daten des Rheins sind hiervon ausgenommen. Es werden Konzentrationsangaben zu verschiedenen Inhalts- resp. Schadstoffen mit Bezug auf die einzelnen Fliessgewässer, sowie der geographischen Koordinaten gemacht.</p><p>Weitere Informationen: <a href="https://www.bs.ch/wsu/aue/abteilung-gewaesser-und-boden#oberflaechengewaesser-und-fischerei" target="_blank">https://www.bs.ch/wsu/aue/abteilung-gewaesser-und-boden#oberflaechengewaesser-und-fischerei</a></p>`
- **Contact_name** `Open Data Basel-Stadt`
- **Issued** `2020-04-06`
- **Modified** `2026-01-27T06:07:34+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `1993-08-23T22:00:00+00:00`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Raum und Umwelt']`
- **Keywords** `['Rhein', 'Messwert', 'Wasserqualität', 'Fluss', 'Chemie', 'Rüs', 'Wassertemperatur']`
- **Publisher** `Amt für Umwelt und Energie`
- **Reference** `None`


# Load packages

```{r}

library(tidyverse)
```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Create directory if it does not exist
  data_path <- file.path(getwd(), '..', 'data')
  if (!dir.exists(data_path)) {
    dir.create(data_path, recursive = TRUE)
  }
  # Download the CSV file
  csv_path <- file.path(data_path , '100066.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
  )
  # if dataframe only has one column or less the data is not ";" separated
  if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
  }
  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100066/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)

head(df)
tail(df)

```

```{r}
# Remove columns that have no values
df <- Filter(function(x) !all(is.na(x)), df)

# Remove rows with missing values (if appropriate)
df <- na.omit(df)
```

```{r}
# display a small random sample transposed in order to see all variables
t(sample_n(df, 5))
```

```{r}
# the size of the data frame in memory
size <- object.size(df)
#  the size in bytes
print(size)
```

```{r}
# describe numerical features
summary(df[, sapply(df, is.numeric)])
```

```{r}
# describe non-numerical features
summary(df[, sapply(df, Negate(is.numeric))])
```

```{r}
# check missing values
df %>%
  mutate(row = row_number()) %>%
  gather(key = "variable", value = "value", -row) %>%
  ggplot(aes(x = variable, y = row)) +
  geom_tile(aes(fill = is.na(value)), color = "black") +
  scale_fill_manual(values = c("TRUE" = "grey", "FALSE" = "red")) +
  labs(x = "", y = "", fill = "Missing") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# plot a histogram for each numerical feature
df %>%
  select_if(is.numeric) %>%
  gather() %>%
  ggplot( aes(value)) +
  geom_histogram(bins = 10, color = "white", fill = "red") +
    facet_wrap(~key, scales = 'free_x')
```

# Continue your code here...

```{r}

```
------------------------------------------------------------------------

# Questions about the data?

Open Data Basel-Stadt | opendata@bs.ch
