---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-25"
output: html_document
---

## Dataset: Standorte Mess-Stationen Smart Climate Luftklima

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100082)

Auto generated R starter code for data set 100082.

## Metadata

- **Dataset_identifier** `100082`
- **Title** `Standorte Mess-Stationen Smart Climate Luftklima`
- **Description** `<p>Der Datensatz zeigt die Standorte der Mess-Stationen für den Datensatz <a href="https://data.bs.ch/explore/dataset/100009" target="_blank">«Luftklima Smart Regio Basel»</a>.</p><p><b>Änderungsprotokoll:</b></p><p><b>18.04.2024:</b> Die Koordinaten werden automatisch plausibilisiert. Es werde nur Koordinaten angezeigt, die in einem bestimmten Umkreis von Basel sind. Der Code dazu ist hier verfügbar: <a href="https://github.com/opendatabs/data-processing/blob/master/meteoblue_wolf/etl.py" target="_blank">https://github.com/opendatabs/data-processing/blob/master/meteoblue_wolf/etl.py</a> </p>`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2020-05-12`
- **Modified** `2024-06-25T13:11:05+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `None`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Raum und Umwelt']`
- **Keywords** `['Wetter', 'Temperatur', 'Regen', 'Niederschlag', 'Sensoren', 'Klima', 'Wolf-Areal', 'Smart City Lab']`
- **Publisher** `meteoblue AG`
- **Reference** `None`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Download the CSV file
  csv_path <- file.path(getwd(), '..', 'data', '100082.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
    read.csv(csv_path, sep = ",", stringsAsFactors = FALSE, encoding = "UTF-8"),
    warning = function(w) NULL,
    error = function(e) NULL
  )

  # If the dataframe has one column or less, try with semicolon as separator
  if (is.null(data) || ncol(data) <= 1) {
    data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
    )

    if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
    }
  }

  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100082/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
