---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-10-04"
output: html_document
---

## Dataset: Coronavirus (COVID-19): Fallzahlen ganze Schweiz

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100077)

Auto generated R starter code for data set 100077.

## Metadata

- **Dataset_identifier** `100077`
- **Title** `Coronavirus (COVID-19): Fallzahlen ganze Schweiz`
- **Description** `<p style="margin-bottom: 1em; background-color: rgb(244, 245, 246);"><font face="Arial, Helvetica, sans-serif"><span style="font-size: 14px;">This dataset is based on the <a href="https://github.com/openZH/covid_19" target="_blank">Github repository organized by OpenZH</a>, its contents are filled by employees of the Cantons and volunteers based on official sources. Data for Basel-Stadt are inserted by <a href="https://opendata.bs.ch" target="_blank">Fachstelle für OGD Basel-Stadt</a> based on the official website of Canton Basel-Stadt. The dataset is refreshed from github every hour, 5 minutes past the hour. Geographical data for the cantons has been added by Opendatasoft in order to produce visualisations. </span></font><br/></p><table class="table table-bordered" style="width: 881px; font-family: Arial, Helvetica, sans-serif; font-size: 14px; background-color: rgb(244, 245, 246);"><tbody><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Field Name</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Description</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Format</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Note<br/></td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">update</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Date and time of notification</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);"> YYYY-MM-DD-HH-MM</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);"><br/></td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">name<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Name of the reporting canton<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Text<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);"><br/></td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">abbreviation_canton_and_fl</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Abbreviation of the reporting canton</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Text</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);"><br/></td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">ncumul_tested</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Reported number of tests performed as of date</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Irrespective of canton of residence</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">ncumul_conf</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Reported number of confirmed cases as of date</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Only cases that reside in the current canton</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">current_hosp (formerly ncumul_hosp) *<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Reported number of hospitalised patients on date</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Irrespective of canton of residence</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">current_icu (formerly ncumul_icu) *<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Reported number of hospitalised patients in ICUs on date</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Irrespective of canton of residence</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">current_vent(formerly ncumul_vent) *<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Reported number of patients requiring ventilation on date</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Irrespective of canton of residence</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">ncumul_released</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Reported number of patients released from hospitals or reported recovered as of date</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Irrespective of canton of residence</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">ncumul_deceased</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Reported number of deceased as of date</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Only cases that reside in the current canton</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">new_hosp *<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number of new hospitalisations since last date<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Number<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Irrespective of canton of residence</td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">source</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Source of the information</td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">URL link<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);"><br/></td></tr><tr><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">geo_point_2d<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">Geographical centroid of the canton<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);">geo_point_2d<br/></td><td style="padding: 0.25em; border-color: rgb(238, 238, 238);"><br/></td></tr></tbody></table><p style="font-family: Arial, Helvetica, sans-serif; margin-bottom: 1em; font-size: 14px; background-color: rgb(244, 245, 246);"><br/></p><p style="font-family: Arial, Helvetica, sans-serif; margin-bottom: 1em; font-size: 14px; background-color: rgb(244, 245, 246);">*<em>These variables were affected by the format change on April 9th, 2020, which consists in:</em></p><p style="font-family: Arial, Helvetica, sans-serif; margin-bottom: 0px; font-size: 14px; background-color: rgb(244, 245, 246);"><em>- new variable "new_hosp"<br/>- variables "ncumul_hosp", "ncumul_icu", "ncumul_vent" have been renamed to "current_hosp", "current_icu", "current_vent", to fit with their nature.<br/>To ensure compatibility with already made dashboards or reuses, these fields have been duplicated to avoid errors when their old names are used; but we strongly recommand to replace their old names by the new as soon as possible.</em></p>`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2020-04-07`
- **Modified** `2023-05-15T08:05:30+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `2020-01-31T23:00:00+00:00`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Gesundheit']`
- **Keywords** `['covid19', 'pandemic', 'pandémie', 'Suisse', 'CH', 'Switzerland', 'coronavirus']`
- **Publisher** `OpenZH`
- **Reference** `https://github.com/openZH/covid_19`


# Load packages

```{r}

library(tidyverse)
```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Create directory if it does not exist
  data_path <- file.path(getwd(), '..', 'data')
  if (!dir.exists(data_path)) {
    dir.create(data_path, recursive = TRUE)
  }
  # Download the CSV file
  csv_path <- file.path(data_path , '100077.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
  )
  # if dataframe only has one column or less the data is not ";" separated
  if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
  }
  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100077/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)

head(df)
tail(df)

```

```{r}
# Remove columns that have no values
df <- Filter(function(x) !all(is.na(x)), df)

# Remove rows with missing values (if appropriate)
df <- na.omit(df)
```

```{r}
# display a small random sample transposed in order to see all variables
t(sample_n(df, 5))
```

```{r}
# the size of the data frame in memory
size <- object.size(df)
#  the size in bytes
print(size)
```

```{r}
# describe numerical features
summary(df[, sapply(df, is.numeric)])
```

```{r}
# describe non-numerical features
summary(df[, sapply(df, Negate(is.numeric))])
```

```{r}
# check missing values
df %>%
  mutate(row = row_number()) %>%
  gather(key = "variable", value = "value", -row) %>%
  ggplot(aes(x = variable, y = row)) +
  geom_tile(aes(fill = is.na(value)), color = "black") +
  scale_fill_manual(values = c("TRUE" = "grey", "FALSE" = "red")) +
  labs(x = "", y = "", fill = "Missing") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# plot a histogram for each numerical feature
df %>%
  select_if(is.numeric) %>%
  gather() %>%
  ggplot( aes(value)) +
  geom_histogram(bins = 10, color = "white", fill = "red") +
    facet_wrap(~key, scales = 'free_x')
```

# Continue your code here...

```{r}

```
------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
