---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-26"
output: html_document
---

## Dataset: Feinstaubmessungen Naturhistorisches Museum Basel

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100100)

Auto generated R starter code for data set 100100.

## Metadata

- **Dataset_identifier** `100100`
- **Title** `Feinstaubmessungen Naturhistorisches Museum Basel`
- **Description** `<p>Im Rahmen der Sonderausstellung <a href="https://www.nmbs.ch/home/ausstellungen/sonderausstellung-ERDE-AM-LIMIT.html" target="_blank">ERDE AM LIMIT</a> (20.11.2020 bis 3.7.2022) wurden mit Hilfe eines Mikrosensors Feinstaub (PM2.5) vom Dach des <a href="https://www.nmbs.ch/" target="_blank">Naturhistorischen Museums Basel</a> gemessen. Hier werden die unvalidierten Daten von Feinstaub PM2.5 zur Verfügung gestellt.</p>`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2020-11-20`
- **Modified** `2024-06-25T22:30:04+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `2020-10-02T13:30:00+00:00`
- **Temporal_coverage_end_date** `2022-06-06T10:30:00+00:00`
- **Themes** `['Raum und Umwelt']`
- **Keywords** `['Luftqualität', 'Feinstaub', 'PM25', 'PM2.5', 'Museum']`
- **Publisher** `Lufthygieneamt beider Basel`
- **Reference** `None`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Create directory if it does not exist
  data_path <- file.path(getwd(), '..', 'data')
  if (!dir.exists(data_path)) {
    dir.create(data_path, recursive = TRUE)
  }
  # Download the CSV file
  csv_path <- file.path(data_path , '100100.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
  )
  # if dataframe only has one column or less the data is not ";" separated
  if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
  }
  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100100/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
