---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-25"
output: html_document
---

## Dataset: Coronavirus (Covid-19): Massentests in Betrieben

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100146)

Auto generated R starter code for data set 100146.

## Metadata

- **Dataset_identifier** `100146`
- **Title** `Coronavirus (Covid-19): Massentests in Betrieben`
- **Description** `<p>Dieser Datensatz zeigt die SARS-CoV-2-Tests, welche an Angestellten von baselstädtischen Betrieben durchgeführt wurden. Es werden die Anzahl durchgeführter Tests sowie die Test-Positivitätsrate pro Woche aufgeführt. Weitere Informationen zum Testen in Betrieben: <a href="https://www.coronavirus.bs.ch/testen/massentests-in-betrieben.html" target="_blank">https://www.coronavirus.bs.ch/testen/massentests-in-betrieben.html</a></p>`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2021-06-10`
- **Modified** `2023-01-17T08:15:41+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `2021-03-28T22:00:00+00:00`
- **Temporal_coverage_end_date** `2023-01-08T23:00:00+00:00`
- **Themes** `['Gesundheit']`
- **Keywords** `['SARS-CoV-2', 'COVID-19', 'Corona', 'Coronavirus', 'Test', 'PCR', 'Firma']`
- **Publisher** `Medizinische Dienste`
- **Reference** `https://www.gesundheit.bs.ch/`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Download the CSV file
  csv_path <- file.path(getwd(), '..', 'data', '100146.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
    read.csv(csv_path, sep = ",", stringsAsFactors = FALSE, encoding = "UTF-8"),
    warning = function(w) NULL,
    error = function(e) NULL
  )

  # If the dataframe has one column or less, try with semicolon as separator
  if (is.null(data) || ncol(data) <= 1) {
    data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
    )

    if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
    }
  }

  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100146/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
