---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-26"
output: html_document
---

## Dataset: Temperatur Wiese

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100269)

Auto generated R starter code for data set 100269.

## Metadata

- **Dataset_identifier** `100269`
- **Title** `Temperatur Wiese`
- **Description** `<p>Der Datensatz zeigt die stündlichen Temperaturwerte der Wiese an.</p><p>Koordinaten: <a href="https://map.geo.bs.ch/s/7z0Q" target="_blank">47.581638577259945, 7.59193858146811</a></p>`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2023-05-15`
- **Modified** `2024-06-26T06:30:04+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `2023-01-24T06:36:00+00:00`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Raum und Umwelt']`
- **Keywords** `['Fluss']`
- **Publisher** `Tiefbauamt`
- **Reference** `None`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Download the CSV file
  csv_path <- file.path(getwd(), '..', 'data', '100269.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
    read.csv(csv_path, sep = ",", stringsAsFactors = FALSE, encoding = "UTF-8"),
    warning = function(w) NULL,
    error = function(e) NULL
  )

  # If the dataframe has one column or less, try with semicolon as separator
  if (is.null(data) || ncol(data) <= 1) {
    data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
    )

    if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
    }
  }

  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100269/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
