---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2025-05-08"
output: html_document
---

## Dataset: Gesundheitsversorgung (GSV): Pflegeheime

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100318)

Auto generated R starter code for data set 100318.

## Metadata

- **Dataset_identifier** `100318`
- **Title** `Gesundheitsversorgung (GSV): Pflegeheime`
- **Description** `Im vorliegenden Datensatz sind Einträge mit dem Attribut "Heimname" zu finden, bei denen der Wert "Alle Pflegeheime" verwendet wird. Diese Bezeichnung dient dazu, Daten zu aggregieren, die die Gesamtheit aller Pflegeheime repräsentieren. Nutzer sollten beachten, dass der Eintrag "Alle Pflegeheime" unter "Heimname" eine kollektive Perspektive auf die Daten darstellt.`
- **Contact_name** `Open Data Basel-Stadt`
- **Issued** `2023-12-15`
- **Modified** `2025-02-26T15:45:44+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `2016-12-31T23:00:00+00:00`
- **Temporal_coverage_end_date** `2023-12-30T23:00:00+00:00`
- **Themes** `['Gesundheit']`
- **Keywords** `None`
- **Publisher** `Statistisches Amt`
- **Reference** `https://www.bs.ch/gd/bereich-gesundheitsversorgung/`


# Load packages

```{r}

library(tidyverse)
```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Create directory if it does not exist
  data_path <- file.path(getwd(), '..', 'data')
  if (!dir.exists(data_path)) {
    dir.create(data_path, recursive = TRUE)
  }
  # Download the CSV file
  csv_path <- file.path(data_path , '100318.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
  )
  # if dataframe only has one column or less the data is not ";" separated
  if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
  }
  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100318/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)

head(df)
tail(df)

```

```{r}
# Remove columns that have no values
df <- Filter(function(x) !all(is.na(x)), df)

# Remove rows with missing values (if appropriate)
df <- na.omit(df)
```

```{r}
# display a small random sample transposed in order to see all variables
t(sample_n(df, 5))
```

```{r}
# the size of the data frame in memory
size <- object.size(df)
#  the size in bytes
print(size)
```

```{r}
# describe numerical features
summary(df[, sapply(df, is.numeric)])
```

```{r}
# describe non-numerical features
summary(df[, sapply(df, Negate(is.numeric))])
```

```{r}
# check missing values
df %>%
  mutate(row = row_number()) %>%
  gather(key = "variable", value = "value", -row) %>%
  ggplot(aes(x = variable, y = row)) +
  geom_tile(aes(fill = is.na(value)), color = "black") +
  scale_fill_manual(values = c("TRUE" = "grey", "FALSE" = "red")) +
  labs(x = "", y = "", fill = "Missing") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# plot a histogram for each numerical feature
df %>%
  select_if(is.numeric) %>%
  gather() %>%
  ggplot( aes(value)) +
  geom_histogram(bins = 10, color = "white", fill = "red") +
    facet_wrap(~key, scales = 'free_x')
```

# Continue your code here...

```{r}

```
------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
