---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-26"
output: html_document
---

## Dataset: Grosser Rat: Zuweisungen von Geschäften

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100312)

Auto generated R starter code for data set 100312.

## Metadata

- **Dataset_identifier** `100312`
- **Title** `Grosser Rat: Zuweisungen von Geschäften`
- **Description** `<p style="font-family: sans-serif;">Dieser Datensatz zeigt Zuweisungen von Geschäften, die im Grossen Rat des Kantons Basel-Stadt behandelt werden.</p><p style="font-family: sans-serif;">Die Daten können auch auf der Webseite des Grossen Rates eingesehen werden:<br/><a href="https://grosserrat.bs.ch/" target="_blank">https://grosserrat.bs.ch</a></p>`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2023-09-28`
- **Modified** `2024-06-26T08:03:49+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `None`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Politik', 'Verwaltung']`
- **Keywords** `['Regierungsrat', 'Grosser Rat', 'Parlament', 'Parlamentarische Vorstösse']`
- **Publisher** `Parlamentsdienst des Grossen Rats`
- **Reference** `https://grosserrat.bs.ch/`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Create directory if it does not exist
  data_path <- file.path(getwd(), '..', 'data')
  if (!dir.exists(data_path)) {
    dir.create(data_path, recursive = TRUE)
  }
  # Download the CSV file
  csv_path <- file.path(data_path , '100312.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
  )
  # if dataframe only has one column or less the data is not ";" separated
  if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
  }
  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100312/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
