---
title: "Open Government Data, provided by Statistisches Amt des Kantons Basel-Stadt - Fachstelle OGD"
date: "2024-06-26"
output: html_document
---

## Dataset: Kitas und Tagesheime

[Direct data shop link for dataset](https://data.bs.ch/explore/dataset/100341)

Auto generated R starter code for data set 100341.

## Metadata

- **Dataset_identifier** `100341`
- **Title** `Kitas und Tagesheime`
- **Description** `«Kitas», «Kindertagesstätten» oder «Tagesheime» sind Einrichtungen, in denen Kinder regelmässig tagsüber durch qualifizierte Fachpersonen und in geeigneten Räumlichkeiten betreut werden.
«Tagesfamilien» sind Familien, in denen Kinder gegen Entgelt und regelmässig in geeigneten Räumlichkeiten betreut werden.`
- **Contact_name** `Fachstelle für OGD Basel-Stadt`
- **Issued** `2024-02-20`
- **Modified** `2024-06-26T05:06:54+00:00`
- **Rights** `NonCommercialAllowed-CommercialAllowed-ReferenceRequired`
- **Temporal_coverage_start_date** `None`
- **Temporal_coverage_end_date** `None`
- **Themes** `['Bevölkerung', 'Geographie', 'Bildung, Wissenschaft']`
- **Keywords** `['Kinder', 'Betreuung', 'Familie', 'Tagesstruktur', 'Horte', 'Mittagstische', 'Tagesfamilie']`
- **Publisher** `Jugend, Familie und Sport`
- **Reference** `www.geo.bs.ch/tagesheime_kitas; https://www.geocat.ch/geonetwork/srv/ger/catalog.search#/metadata/c6efbfc6-e156-4f98-836b-d5c89ac9d6e5`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

The dataset is read into a dataframe

```{r}
get_dataset <- function(url) {
  # Download the CSV file
  csv_path <- file.path(getwd(), '..', 'data', '100341.csv')
  download.file(url, csv_path, mode = "wb")

  # Read the CSV file
  data <- tryCatch(
    read.csv(csv_path, sep = ",", stringsAsFactors = FALSE, encoding = "UTF-8"),
    warning = function(w) NULL,
    error = function(e) NULL
  )

  # If the dataframe has one column or less, try with semicolon as separator
  if (is.null(data) || ncol(data) <= 1) {
    data <- tryCatch(
      read.csv(csv_path, sep = ";", stringsAsFactors = FALSE, encoding = "UTF-8"),
      warning = function(w) NULL,
      error = function(e) NULL
    )

    if (is.null(data) || ncol(data) <= 1) {
      stop("The data wasn't imported properly. Very likely the correct separator couldn't be found.\nPlease check the dataset manually and adjust the code.")
    }
  }

  return(data)
}
```

```{r}

df <- get_dataset('https://data.bs.ch/explore/dataset/100341/download?format=csv&timezone=Europe%2FZurich')

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle für OGD Basel-Stadt | opendata@bs.ch
